---
title: 'Programming Assignment 2: Google PageRank'
author: "Yu-Wen Chen & Harsh Rajeshkumar Shah"
date: "2020/9/17"
output: html_document
---


#### a. Determine the corresponding transition matrix A.
```{r }
#Corresponding transition matrix of (a)
Aa<-matrix(c(0,1/3,1/3,1/3,0,0,1/2,1/2,1,0,0,0,1/2,0,1/2,0),nrow=4)

#Pint out the matrix (a)
print(Aa)

#Corresponding transition matrix of (b)
Ab<-matrix(c(0,1/3,1/3,1/3,0,0,0,0,1/2,1/2,1,0,0,0,0,0,1/2,1/2,0,0,0,0,0,0,1),nrow=5)

#Pint out the matrix (b)
print(Ab)

```
#### b.  Determine the google matrix G
```{r}
#(1)Google matrix of (a)
#According to the formula: G=(1-p)P+pK, p=0.15
#We need to determine the matrix K for a first
Ka<-matrix(c(rep(1/4,16)),nrow=4)

#Then determine the Google matrix of (a)
Pa=Aa
Ga<-matrix(c(0.85*Pa+0.15*Ka),nrow=4)

#Pint out the Google matrix of (a)
print(Ga)

#(2)Google matrix of (b)
#Determine the matrix K for b first
Kb<-matrix(c(rep(1/5,25)),nrow=5)

#Determine the matrix P for b because there are dangling node in b
Pb<-matrix(c(0,1/3,1/3,1/3,0,0,0,0,1/2,1/2,1,0,0,0,0,0,1/2,1/2,0,0,1/5,1/5,1/5,1/5,1/5),nrow=5)

#Then determine the Google matrix of (b)
Gb<-matrix(c(0.85*Pb+0.15*Kb),nrow=5)

#Pint out the Google matrix of (b)
print(Gb)

```

#### c. Does either graph have a dangling node? If so which one(s)?
```{r}
#Testing is there any dangling node in a graph
#Check the probability of a after 60 step
library(expm)

Aa%^%60
Aa_eig<-eigen(Aa)
Aa_eig$vectors[,1]/sum(Aa_eig$vectors[,1])

#Check the probability of b after 50 and 51 step
Ab%^%39
Ab%^%40

Ab_eig<-eigen(Ab)
Ab_eig$vectors[,1]/sum(Ab_eig$vectors[,1])

```
#### According to the result, the graph (b) has a dangling nodes which is states 5.




#### d. Does either graph have a disconnected node? If so which one(s)?

```{r}
Aa_eig<-eigen(Aa)


adis<-sweep(Aa_eig$vectors,MARGIN = 2,colSums(Aa_eig$vectors),"/")
adis

Ab_eig<-eigen(Ab)


bdis<-sweep(Ab_eig$vectors,MARGIN = 2,colSums(Ab_eig$vectors),"/")
bdis
```
#### According to the result, there is no disconnected node in neither of them.



#### e. Compute the PageRank of each page in the set. (Recall that the PageRank vector for a web graph with transition matrix A, and damping factor p, is the unique probabilistic eigenvector of the matrix G, corresponding to the eigenvalue 1.)
```{r}
#According to the formula:G=(1-p)A+pK ,(G-λI)q=0, λ=eigenvalue=1, q=steady-state vector

#(a)
#Using  the Google matrix of (a) to calculate the eigenvalue and the eigenvector
Ga_eig<-eigen(Ga)

#print out the eigenvalue and eigenvector
print(Ga_eig)

#Calculate the steady-state vector which is also the PageRank
Ga_eig$vectors[,1]/sum(Ga_eig$vectors[,1])

#(b)
#Using the Google matrix of (b) to calculate the eigenvalue and the eigenvector
Gb_eig<-eigen(Gb)

#print out the eigenvalue and eigenvector
print(Gb_eig)

#Calculate the steady-state vector which is also the PageRank
Gb_eig$vectors[,1]/sum(Gb_eig$vectors[,1])


```
#### (a)PageRank   p1<-0.3681507+0i p2<-0.1418094+0i p3<-0.2879616+0i p4<-0.2020783+0i
#### According to PageRank, the most important page in the graph a is page 3. The complete rank in is page 3,1,4, and 2.

#### (b)PageRank   p1<-0.2315348;p2<-0.2085167 ;p3<-0.2085167 ;p4<-0.2085167;p5<-0.1429152

#### According to PageRank, the most important page in graph b is pages 2,3,4. The complete rank is pages 2 and 3 and 4,1, and 5.

